Type Evolution in Interactive Programming Systems

### 2024-06-01 paper.tex
\affiliation is required

\author[a]{Jonathan Edwards}%[0000-0003-1958-7967]
\authorinfo{is an independent researcher. Contact him at \email{jonathanmedwards@gmail.com}.}
\affiliation[a]{Independent, Boston, MA, USA}

\author[b]{Tomas Petricek}%[0000-0002-7242-2208]
\authorinfo{is an Associate Professor at Charles University. Contact him at \email{tomas@tomasp.net}.}
\affiliation[b]{Charles University, Prague, Czechia}

\author[c,d]{Tijs van der Storm}%[0000-0001-8853-7934]
\authorinfo{is a Senior Researcher at Centrum Wiskunde \&\ Informatica (CWI) and a Professor at the University of Groningen. Contact him at \email{storm@cwi.nl}.}
\affiliation[c]{Centrum Wiskunde \&\ Informatica (CWI), Amsterdam, Netherlands}
\affiliation[d]{University of Groningen, Groningen, Netherlands}

\author[e]{Geoffrey Litt}%[0000-0003-0858-5165]
\authorinfo{is a Senior Researcher at the independent research lab Ink \& Switch. Contact him at \email{gklitt@gmail.com}.}
\affiliation[e]{Ink \& Switch, Planet Earth}

\authorrunning{J. Edwards, T. Petricek, T. van der Storm, G. Litt}

>>>>

\author{Anonymous}
\affiliation{blinded}
% \author[a]{Jonathan Edwards}%[0000-0003-1958-7967]
% \authorinfo{is an independent researcher. Contact him at \email{jonathanmedwards@gmail.com}.}
% \affiliation[a]{Independent, Boston, MA, USA}

% \author[b]{Tomas Petricek}%[0000-0002-7242-2208]
% \authorinfo{is an Associate Professor at Charles University. Contact him at \email{tomas@tomasp.net}.}
% \affiliation[b]{Charles University, Prague, Czechia}

% \author[c,d]{Tijs van der Storm}%[0000-0001-8853-7934]
% \authorinfo{is a Senior Researcher at Centrum Wiskunde \&\ Informatica (CWI) and a Professor at the University of Groningen. Contact him at \email{storm@cwi.nl}.}
% \affiliation[c]{Centrum Wiskunde \&\ Informatica (CWI), Amsterdam, Netherlands}
% \affiliation[d]{University of Groningen, Groningen, Netherlands}

% \author[e]{Geoffrey Litt}%[0000-0003-0858-5165]
% \authorinfo{is a Senior Researcher at the independent research lab Ink \& Switch. Contact him at \email{gklitt@gmail.com}.}
% \affiliation[e]{Ink \& Switch, Planet Earth}

% \authorrunning{J. Edwards, T. Petricek, T. van der Storm, G. Litt}
